Mining Planet Search Data for Binary Stars: The $\psi^1$ Draconis system

### 2015-10-22 paper/ms.tex
Updated url to new repository name.

%\tablecomments{The velocities given here are shifted into the system velocity rest frame using the results of the analysis presented in Section \ref{sec:orbit}. The raw radial velocity data is available at \url{https://github.com/kgullikson88/Planet-Finder}}
\end{deluxetable}

@@

\begin{deluxetable}{rl}
\tabletypesize{\footnotesize}
\tablewidth{0pt}
\tablenum{2}
\tablecaption{ Orbital parameters for the $\psi^1$ Draconis A subsystem. }
%\tablehead{
%\colhead{Component} & \colhead{$T_{\rm eff}$} & \colhead{$\log{g}$} & \colhead{{[}Fe/H{]}}& \colhead{$M (M_{\odot})$} }

@@

This method could be used to search for the spectral lines of stellar companions to other stars observed with high--precision radial--velocity surveys. To that end, and in the goal of open science, we make the source code used for the analysis and generating the plots for this paper available at \url{https://github.com/kgullikson88/Planet-Finder}. The raw radial--velocity measurements for both the primary and secondary star, as well as the MCMC chains, are available at the same url.

>>>>

\end{deluxetable}

@@

\begin{deluxetable}{rl}
\tabletypesize{\footnotesize}
\tablewidth{0pt}
\tablenum{2}
\tablecaption{ Orbital parameters for the $\psi^1$ Draconis A subsystem. }

@@

This method could be used to search for the spectral lines of stellar companions to other stars observed with high--precision radial--velocity surveys. To that end, and in the goal of open science, we make the source code used for the analysis and generating the plots for this paper available at \url{https://github.com/kgullikson88/Companion-Finder}. The raw radial--velocity measurements for both the primary and secondary star, as well as the MCMC chains, are available at the same url.
